Visualizing Functional Data

### 2017-08-14 paper/sections/categorical.tex
zhang correlation maps, start

 While a table is encouraged for a small number of variables
 \cite{munznertablesgood}), bar graphs and histograms are typically used to display
 differences between subsets such as \d_0,\dots, \d_n
 \cite{ioannidis_history_2003-1, friendly_brief_2006}. Variations on histograms
 include the hanging rootgram, ord plot, and other distribution oriented
 plots \cite{tukey_exploratory_1977, friendly_visualizing_2000}.

 While conditional  distributions can somewhat be visualized using Fourfold displays,
 Mosiac displays, and using logit models, these plots have somewhat limited
 dimensionality and are somewhat limited to 3 sets of categories
 \cite{friendly_visualizing_2000}. Another approach is to [insert correlation
   paper here...]

@@

\begin{figure}
  \includegraphics{parallelsets.png}
  \caption{On the left is the categorical view, where users can define
    categories based on other categorical information. For example, in this
    veiw working family with children is defined as a household with one or
    more children. On the right is a parallel coordinate graph wherin the
    dominiant category informs the colors, the size of the box is relative to
    ghe category size, and the historgrams show the freqiencies of those
    categories relative to the connecting catgories (market type and income
    respectively). }
  \label{fig:upsetfig1}
\end{figure}
While UpSet is designed with all sorts of sets in mind, the Parallel Sets tool
showin in figure~\ref{fig:upsetfig} is expicilitly designed to show frequencies of set membership in heirarichal
ordered categorical sets, so the \{d_0, \dots, d_n} \in D
  \cite{kosara_parallel_2006}. Building on the fexible linked axis version of
  the parallel cooridnates plot \cite{flexible linked axis}, Parallel Sets
  treats each categorical set independantly but indicates conditional
  dependency through cross tabulations and by grouping the data, indicated via
  color, based on an active dimension that then becomes the pivot point for the
  cross tabulations. In Parallel Sets, quantative data is converted to
  categorical via binning.

>>>>

 While a table is encouraged for a small number of variables
 \cite{munznertablesgood}), bar graphs and histograms are typically used to display
 differences between subsets such as \d_0,\dots, \d_n
 \cite{ioannidis_history_2003-1, friendly_brief_2006}. Variations on histograms
 include the hanging rootgram, ord plot, and other distribution oriented
 plots \cite{tukey_exploratory_1977, friendly_visualizing_2000}. While conditional  distributions can somewhat be visualized using Fourfold displays, Mosiac displays, and using logit models, these plots have somewhat limited dimensionality and are somewhat limited to 3 sets of categories
 \cite{friendly_visualizing_2000}.

@@

\begin{figure}
  \includegraphics{parallelsets.png}
  \caption{On the left is the categorical view, where users can define
    categories based on other categorical information. For example, in this
    veiw working family with children is defined as a household with one or
    more children. On the right is a parallel coordinate graph wherin the
    dominiant category informs the colors, the size of the box is relative to
    ghe category size, and the historgrams show the freqiencies of those
    categories relative to the connecting catgories (market type and income
    respectively). }
  \label{fig:upsetfig1}
\end{figure}

Another important factor in visualizing categorical data is retaining the
inherent heirachy in many datasets with categorical measurements
\cite{shneiderman_visualizing_2000}. The Parallel Sets tool
showin in figure~\ref{fig:upsetfig} is expicilitly designed to show frequencies
of set membership in heirarichal ordered categorical sets, so the \{d_0, \dots, d_n} \in D
  \cite{kosara_parallel_2006}. Building on the fexible linked axis version of
  the parallel cooridnates plot \cite{flexible linked axis}, Parallel Sets
  treats each categorical set independantly but indicates conditional
  dependency through cross tabulations and by grouping the data, indicated via
  color, based on an active dimension that then becomes the pivot point for the
  cross tabulations. In Parallel Sets, quantative data is converted to
  categorical via binning.

\begin{figure}

\end{figure}
Often though it's important to retain the internel structure of the
quantative data, such as when it has internal structucture such as time and
space. Zhang et al propose a method that retains data and allows for
visualizing more than just pairwise relationships\cite{zhang_visual_2015}. Thei
